### 2015-05-24 docs/report/map_serial_vs_parallel.tex
Fixes for map serial vs parallel cmp

In this regard, the more complex the computation to be performed on each array element the better the parallel implementation will perform. That is because in the parallel case, the source \ttarray{} must be copied to sub-arrays in order to be transferred. On the contrary, the serial implementation operates on elements during that time. To observe the effects of this, we also perform the same benchmark using \tstarray{}s.

@@

\note{Unlike other benchmarks in which we were comparing different ways to achieve the same result, this benchmark compares a single way with a changing amount of elements. For that reason, the original charts are not displayed.}

The results for the benchmark are displayed in Figure~\ref{fig:map-par-vs-seq}.
\img{Relative performance of parallel implementation with regards to sequential one using ArrayBuffers}{../../spikes/3.1.3/comparison/chart}{fig:map-par-vs-seq}

@@

\note{Unlike other benchmarks in which we were comparing different ways to achieve the same result, this benchmark compares a single way with a changing amount of elements. For that reason, the original charts are not displayed.}

The results for the benchmark are displayed in Figure~\ref{fig:map-par-vs-seq-shared}.
\img{Relative performance of parallel implementation with regards to sequential one using SharedArrayBuffers}{../../spikes/3.1.3/comparison/chartShared}{fig:map-par-vs-seq-shared}

\subsection{Conclusion}
A couple of interesting findings result from the experiments. An expected one is that the amount of operations per second that can be performed with a serial implementation is almost inversely proportional to the amount of items to transform with a ratio of 1. On the other hand, this is not the case for the parallel approach.

An acceptable speedup of approximately \textbf{2.4x} can be achieved with a relatively large amount of items (\(10E6\)) and performing a computationally expensive computation (generating pseudo-random numbers). Larger speedups might be possible by applying optimizations to the library and there might also be some potential improvements for operations with \tsabuffer{}s as they are likely not fully optimized, being that they are only an experimental feature in Firefox Nightly.

The speedup obtained without shared memory is relative small (approximately \textbf{1.2x}) when compared to that obtained with shared memory. That can be explained by the overhead of copying arrays elements, to work around the lack of shared memory, when communicating with the Web Workers.

>>>>

In this regard, the more complex the computation to be performed on each array element, the better the parallel implementation will perform. That is because, in the parallel case, the source \ttarray{} must be copied to sub-arrays in order to be transferred. On the contrary, the serial implementation operates on elements during that time. To observe the effects of this difference, we also perform the same benchmark using \tstarray{}s.

@@

\note{Unlike other benchmarks in which we were comparing different ways to achieve the same result, this benchmark compares a single way with a varying amount of elements. For that reason, the original charts are not displayed.}

The results for the benchmark are displayed in Figure~\ref{fig:map-par-vs-seq}.
\img{Relative performance of parallel implementation with regards to sequential one using \tabuffer{}s}{../../spikes/3.1.3/comparison/chart}{fig:map-par-vs-seq}

@@

The results for the benchmark are displayed in Figure~\ref{fig:map-par-vs-seq-shared}.
\img{Relative performance of parallel implementation with regards to sequential one using \tsabuffer{}s}{../../spikes/3.1.3/comparison/chartShared}{fig:map-par-vs-seq-shared}

\subsection{Conclusion}
A couple of interesting findings result from the experiments. An expected one is that the amount of operations per second that can be performed with a serial implementation is almost inversely proportional to the amount of items to transform (with a ratio of 1). On the other hand, this is not the case for the parallel approach.

An acceptable speedup of approximately \textbf{2.4x} can be achieved with a relatively large amount of items (\(10E6\)) and performing a computationally expensive operation (generating pseudo-random numbers). Larger speedups might be possible by applying optimizations to the library and there might also be some potential improvements for operations with \tsabuffer{}s as they are likely not fully optimized, being that they are only an experimental feature in Firefox Nightly.

The speedup obtained without shared memory is relative small (approximately \textbf{1.2x}) when compared to that obtained with shared memory. That can be explained by the overhead of copying array elements, to work around the lack of shared memory, when communicating with the Web Workers.
